\batcave: Bayesian Analysis Tools for Context-Aware Variant Evaluation

### 2019-09-24 NAR_DRAFT.tex
some calibration stuff

>>>>

We focus on the calibration benefits of \batcave because calibration is important for both clinical and research communities.
\begin{itemize}
  \item Research/Discovery
  \begin{itemize}
    \item Manual review is time consuming, and the number of mutations can be overwhelming at lower frequencies. Calibration reduces wasted effort.
    \item Drug discovery is expensive and effort must be focused. Finding common low frequency alleles is important, and having a calibrated probability for each tumor a variant is found in would be useful.
  \end{itemize}
  \item clinical
  \begin{itemize}
    \item many resistance mutations are present at low frequencies in primary tumor. If a tumor is sequenced and you can assign a probability to the mutation, it may be possible to indicate treatment with the drug for the resistance mutation simultaneous to the first line treatment. For instance if the mutation has a 80\% probabiliity of being present, yes, but if 20\% no. Balance of harm from treating for a mutation that isn't there.
  \end{itemize}

\end{itemize}
